Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-23 analysis/paper/paper.Rmd
Edits to paper

Sheath blight (SB) disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B. Frank) Donk.] of rice is an economically important disease worldwide, which can cause up to 44% yield losses [@Marchetti1991] under conducive conditions.

@@

Sheath blight is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications [@Rush1983; @Groth2008], nitrogen management [@Castilla1996; @Slaton2003; @Tang2007] and water management [@Castilla1996]. We therefore established field experiments in order to determine what effects AWD and N had upon SB incidence and severity.

@@

Disease scoring was the same in both experiments using the same disease assessment scale for field evaluation developed at IRRI where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%. Where severity was considered to be the amount of leaf or sheath tissue covered by SB lesions. Two sample areas per plot (1m x 1m) were assessed. For nine hills per sample, the number of tillers per hill and number of tillers with SB (incidence) were measured. Tiller SB severity was measured for four tillers per hill and six leaves tiller using the rating scale. Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.

@@

In 2015 the incidence of tiller SB remained low throughout the growing season only reaching 15% in 2015 in the N~2~, flooded treatment (Figure \@ref(fig:figure-1)). The nitrogen treatments, N~1~ and N~2~, were both significantly different when compared with the control N~0~ treatment. However, water management was not significantly different.

@@

In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf SB severity.

>>>>

Sheath blight (ShB) disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B. Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas. The disease can cause up to 44% yield losses [@Marchetti1991] under conducive conditions.

Sheath blight is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen management [@Castilla1996; @Slaton2003; @Tang2007] and water management [@Castilla1996].

@@

Because of the interactions between irrigation and N, we established field experiments in order to determine what effects AWD and N had upon ShB incidence and severity.

@@

Disease scoring was the same in both experiments using the same disease assessment scale for field evaluation developed at IRRI where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%. Where severity was considered to be the amount of leaf or sheath tissue covered by ShB lesions. Two sample areas per plot (1m x 1m) were assessed. For nine hills per sample, the number of tillers per hill and number of tillers with ShB (incidence) were measured. Tiller ShB severity was measured for four tillers per hill and six leaves tiller using the rating scale. Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.

@@

In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N~2~, flooded treatment (Figure \@ref(fig:figure-1)). The nitrogen treatments, N~1~ and N~2~, were both significantly different when compared with the control N~0~ treatment. However, water management was not significantly different.

@@

In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf ShB severity.
